---
title: "Test"
author: "Emma Chi"
date: "5/30/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
load("cardiovascular.Rdata")
source("CrossValidation_RF.R")
```

```{r}
X
```

We will use a mixed level fractional factorial design. The factors that will have three levels in the design of our experiment are:

- ntree
- nodesize
- cutoff

As there are 7 factors, this means that we must provide one additional factor for each of the factors with three levels. This means we will have a total of 10 factors total

As such, the three level factors will have variable encoding "A" and "B." 

- A `-` for both `ntreeA` and `ntreeB` indicates 100 trees, A `+` for either `ntreeA` or `ntreeB` indicates 550 trees, A `+` for both `ntreeA` and `ntreeB` indicates 1000 trees.

- A `-` for both `nodesizeA` and `nodesizeB` indicates 1, A `+` for either `nodesizeA` or `nodesizeB` indicates 6, A `+` for both `nodesizeA` and `nodesizeB` indicates 11.

- A `-` for both `cutoffA` and `cutoffB` indicates a value of 0.2, A `+` for either `cutoffA` or `cutoffB` indicates a value of 0.5, A `+` for both `cutoffA` and `cutoffB` indicates 0.8.

```{r}
library(FrF2)
frfact.design <- FrF2(nruns = 32, nfactors = 10, randomize = F, factor.names = c("ntreeA", "ntreeB", "replace", "mtry", "nodesizeA", "nodesizeB", "maxnodes", "classwt", "cutoffA", "cutoffB"))
D.one <- desnum(frfact.design) # Extract the design.
print(D.one)
```

```{r}
cat("Generators of the design \n")
generators(frfact.design)
cat("Alias structure \n")
design.info(frfact.design)$aliased
cat("Resolution and word length pattern \n")
design.info(frfact.design)$catlg.entry
```

```{r}
library(corrplot)
X.two <- model.matrix(~(.)^2, data.frame(D.one))

# Create color map on pairwise correlations.
contrast.vectors.correlations.two <- cor(X.two)
corrplot(contrast.vectors.correlations.two, type = "full", addgrid.col = "gray",
         tl.col = "black", tl.srt = 90, method = "color", tl.cex=0.5)
```


# Optimal Design

```{r}
library(AlgDesign)
candidate.set <- gen.factorial(levels=2, nVars = 10, 
                              varNames = c("ntreeA", "ntreeB", "replace", "mtry", "nodesizeA", "nodesizeB", "maxnodes", "classwt", "cutoffA", "cutoffB"))
alternative.design <- optFederov(~ntreeA + ntreeB + replace + mtry+ nodesizeA + nodesizeB + maxnodes + classwt + cutoffA + cutoffB, candidate.set, nTrials = 35, nRepeats = 100)
print.data.frame(alternative.design$design)
```

```{r}
X.two <- model.matrix(~(.)^2-1, data.frame(alternative.design$design))

# Create color map on pairwise correlations.
contrast.vectors.correlations.two <- cor(X.two)
corrplot(contrast.vectors.correlations.two, type = "full", addgrid.col = "gray",
         tl.col = "black", tl.srt = 90, method = "color", tl.cex=0.5)
```


```{r}
# Creating argument design from fractional factorial design
argumentdesign <- data.frame(D.one)
argumentdesign$ntree[argumentdesign$ntreeA == 1 | argumentdesign$ntreeB == 1] <- 550
argumentdesign$ntree[argumentdesign$ntreeA == -1 & argumentdesign$ntreeB == -1] <- 100
argumentdesign$ntree[argumentdesign$ntreeA == 1 & argumentdesign$ntreeB == 1] <- 1000

argumentdesign$nodesize[argumentdesign$nodesizeA == 1 | argumentdesign$nodesizeB == 1] <- 6
argumentdesign$nodesize[argumentdesign$nodesizeA == -1 & argumentdesign$nodesizeB == -1] <- 1
argumentdesign$nodesize[argumentdesign$nodesizeA == 1 & argumentdesign$nodesizeB == 1] <- 11

argumentdesign$cutoff[argumentdesign$cutoffA == 1 | argumentdesign$cutoffB == 1] <- 0.5
argumentdesign$cutoff[argumentdesign$cutoffA == -1 & argumentdesign$cutoffB == -1] <- 0.2
argumentdesign$cutoff[argumentdesign$cutoffA == 1 & argumentdesign$cutoffB == 1] <- 0.8

argumentdesign$replace[argumentdesign$replace == -1] <- 0

argumentdesign$mtry[argumentdesign$mtry == -1] <- 2
argumentdesign$mtry[argumentdesign$mtry == 1] <- 6

argumentdesign$maxnodes[argumentdesign$maxnodes == -1] <- 10
argumentdesign$maxnodes[argumentdesign$maxnodes == 1] <- 1000

argumentdesign$classwt[argumentdesign$classwt == -1] <- 0.5
argumentdesign$classwt[argumentdesign$classwt == 1] <- 0.9

argumentdesign <- data.frame("ntree" = argumentdesign$ntree, "mtry" = argumentdesign$mtry, "replace" = argumentdesign$replace, "nodesize" = argumentdesign$nodesize, "classwt" = argumentdesign$classwt, "cutoff" = argumentdesign$cutoff, "maxnodes" = argumentdesign$maxnodes)
```

```{r}
results <- cv.rf(argumentdesign, y, X)
```

```{r}
results
```

Question 4: Commercial Design
```{r}
run <- c(1:22)
ntree <- c(100, 550, 1000,1000,1000,100, 1000, 100, 100, 100,100, 1000, 100, 550, 100, 1000, 1000, 1000, 100, 1000, 550, 550)
replace <- c(1, 0, 1, 1, 0, 0,0, 0, 1, 0, 0, 1, 1, 0, 0, 0, 0, 1, 1, 1, 1, 1)
mtry <- c(2, 2, 4, 6, 6, 2, 2, 2, 6, 6, 4, 2, 6, 4, 6, 6, 2, 6, 2, 2, 4, 6)
nodesize <- c(11, 1, 1, 1, 1, 1, 6, 11, 1, 1, 11, 11, 6, 6, 11, 11, 11, 11, 1, 1, 6, 11)
maxnodes <- c(10, 10, 10, 1000, 1000, 1000, 10, 10, 10, 10, 1000, 1000, 1000, 505, 505, 10, 1000, 10, 1000, 505, 505, 1000)
classwt <- c(0.5, 0.5, 0.5, 0.5, 0.9, 0.5, 0.9, 0.9, 0.7, 0.9, 0.9, 0.5, 0.5, 0.7, 0.5, 0.5, 0.7, 0.9, 0.9, 0.9, 0.7, 0.9)
cutoff <- c(0.8, 0.2, 0.2, 0.8, 0.2, 0.8, 0.8, 0.2, 0.8, 0.5, 0.8, 0.5, 0.2, 0.5, 0.2, 0.8, 0.2, 0.2, 0.2, 0.8, 0.5, 0.8)

commercial.data <- data.frame("run" = as.factor(run), "ntree" = as.factor(ntree), "replace" = as.factor(replace), "mtry" = as.factor(mtry), "nodesize" = as.factor(nodesize), "maxnodes" = as.factor(maxnodes), "classwt" = as.factor(classwt), "cutoff" = as.factor(cutoff))
print(commercial.data)
```


```{r}
candidate.set2 <- gen.factorial(levels=3, nVars = 7, 
                              varNames = c("ntree", "replace", "mtry", "nodesize", "maxnodes", "classwt", "cutoff"))
comm.opt <- optFederov(~ntree + replace + mtry + nodesize + maxnodes + classwt + cutoff, candidate.set2, nTrials = 22, nRepeats = 100)
print.data.frame(comm.opt$design)
```

```{r}
library(corrplot)
X.three <- model.matrix(~(.)^2-1, data.frame(comm.opt$design))

# Create color map on pairwise correlations.
contrast.vectors.correlations.three <- cor(X.three)
corrplot(contrast.vectors.correlations.three, type = "full", addgrid.col = "gray",
         tl.col = "black", tl.srt = 90, method = "color", tl.cex=0.5)
```

